Realizability-Preserving DG-IMEX Method for the Two-Moment Model of Fermion Transport \tnoteref{support}

### 2018-02-02 Documents/M1/realizableFermionicM1/sections/realizability.tex
Added the caption of Figure 2

\begin{figure}
  \centering
  \begin{tabular}{cc}
    \includegraphics[width=0.5\textwidth]{figures/MabWithBLME}
    \includegraphics[width=0.5\textwidth]{figures/MabWithCBME} \\
    \includegraphics[width=0.5\textwidth]{figures/MabWithBLKS}
    \includegraphics[width=0.5\textwidth]{figures/MabWithMI}
  \end{tabular}
  \caption{}
  \label{fig:MabWithDifferentClosure}
\end{figure}

%\begin{figure}[h!]
%  \begin{subfigure}[b]{0.5\textwidth}
%    \includegraphics[width=\textwidth]{figures/MabWithMI}
%    \caption{$\vect{\cM}_{ab}$ with Minerbo closure.}
%  \end{subfigure}
%  %
%  \begin{subfigure}[b]{0.5\textwidth}
%    \includegraphics[width=\textwidth]{figures/MabWithBLKS}
%    \caption{$\vect{\cM}_{ab}$ with Kershaw closure.}
%  \end{subfigure}
%  \begin{subfigure}[b]{0.5\textwidth}
%    \includegraphics[width=\textwidth]{figures/MabWithCBME}
%    \caption{$\vect{\cM}_{ab}$ with Chernohorsky \& Bludman maximum entropy closure.}
%  \end{subfigure}
%  \begin{subfigure}[b]{0.5\textwidth}
%    \includegraphics[width=\textwidth]{figures/MabWithBLME}
%    \caption{$\vect{\cM}_{ab}$ with Banach \& Larecki maximum entropy closure.}
%  \end{subfigure}
%  \label{fig:MabWithDifferentClosure}
%\end{figure}

>>>>

\begin{figure}[h]
  \centering
  \begin{tabular}{cc}
    \includegraphics[width=0.5\textwidth]{figures/MabWithBLME}
    \includegraphics[width=0.5\textwidth]{figures/MabWithCBME} \\
    \includegraphics[width=0.5\textwidth]{figures/MabWithBLKS}
    \includegraphics[width=0.5\textwidth]{figures/MabWithMI}
  \end{tabular}
   \caption{Illustration of $\vect{\cM}_{ab}$ with four different closures: Banach \& Larecki maximum entropy closure (left top), Chernohorsky \& Bludman maximum entropy closure (right top), Kershaw closure (left bottom), and Minerbo closure (right bottom).
   Total $10^{6}$ pairs of random Fermi-Dirac distribution were generated.
   With these pairs, $\vect{\cM}_{ab}$ with different closures were calculated separately and marked with light-blue points.
   Black lines define the boundary of $\cR$: $\gamma(\vect{\cM}) = 0$.}
  \label{fig:MabWithDifferentClosure}
\end{figure}
